### 2025-10-16 submissions/03-jpam-RR/manuscript_online_appendix.tex
Save local work before reconnecting

\begin{figure}[H]
    \centering
    \caption{Scatter Plot of Proportion Subjectively Asian on Bias}
    \label{scatter-plot-1}
    \begin{subfigure}{.9\textwidth}
    \caption{Year < 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-less2015.png}
    \end{subfigure}
    \centering
    %Second graph
    \begin{subfigure}{.9\textwidth}
    \caption{Year $\geq$ 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-great2015.png}
    \end{subfigure}
    \caption*{\footnotesize{Here are two scatter plots showing the relationship between bias and subjective Asian population in a state. Each dot represents a state in a certain year. Percent subjectively Asian = $\frac{\# \text{Asian}}{\text{Population}}$ \\
    \emph{Source.} 2004-2021 Current Population Survey.}}
    \end{figure}

>>>>

% =========================
% 42: Interaction Coefficient Plots (AW/WA)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Interaction Effects of Anti-Asian Bias with Gender and Parental Education: By Mixed Parental Types Among Adults}
\label{fig:interaction-coefs-aw-wa}

\begin{subfigure}{.48\textwidth}
\caption{Asian Fathers-White Mothers}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_AW.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{White Fathers-Asian Mothers}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_WA.png}
\end{subfigure}

\caption*{\footnotesize{I show interaction coefficients from estimating equation (\ref{eq:identity_reg_bias}) with interaction terms for gender and parental education. I include region $\times$ year fixed effects with controls for sex, quartic age, years of education, and the inverse hyperbolic sine of income. The dependent variable is self-reported Asian identity and the independent variables include demeaned state-level bias interacted with gender and parental education indicators. Each panel results from separate regressions on different samples divided by mixed parental types. Standard errors are clustered on the state level. The samples include second-generation Asian individuals ages 18 and above with mixed-race parentage. Native-born second-generation Asian immigrant individuals with one parent born in an Asian country and one parent born outside of Asia.}}
\end{figure}
\end{center}

% =========================
% 43: Interaction Coefficient Plots (Third Generation by Grandparent Type)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Interaction Effects of Anti-Asian Bias with Gender and Parental Education: By Asian Grandparent Count Among Third Generation}
\label{fig:interaction-coefs-thirdgen-grandparent}

\begin{subfigure}{.45\textwidth}
\caption{One Asian Grandparent}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_OneAsian.png}
\end{subfigure}
\hfill
\begin{subfigure}{.45\textwidth}
\caption{Two Asian Grandparents}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_TwoAsian.png}
\end{subfigure}

\vspace{0.5cm}

\begin{subfigure}{.45\textwidth}
\caption{Three Asian Grandparents}
\centering
\includegraphics[width=1\linewidth]{interaction_coefficients_ThreeAsian.png}
\end{subfigure}

\caption*{\footnotesize{I show interaction coefficients from estimating equation (\ref{eq:identity_reg_bias}) with interaction terms for gender and parental education on third-generation samples. I include region $\times$ year fixed effects with controls for sex, quartic age, years of education, and the inverse hyperbolic sine of income. The dependent variable is self-reported Asian identity and the independent variables include demeaned state-level bias interacted with gender and parental education indicators. Each panel results from separate regressions on different samples divided by the number of Asian grandparents. Standard errors are clustered on the state level. The samples include third-generation Asian individuals with varying degrees of Asian ancestry through grandparents. Native-born third-generation individuals with at least one grandparent born in an Asian country.}}
\end{figure}
\end{center}

\begin{figure}[H]
    \centering
    \caption{Scatter Plot of Proportion Subjectively Asian on Bias}
    \label{scatter-plot-1}
    \begin{subfigure}{.9\textwidth}
    \caption{Year < 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-less2015.png}
    \end{subfigure}
    \centering
    %Second graph
    \begin{subfigure}{.9\textwidth}
    \caption{Year $\geq$ 2015}
    \centering
    \includegraphics[width=.9\linewidth]{scatter-plot-bias-Asian-great2015.png}
    \end{subfigure}
    \caption*{\footnotesize{Here are two scatter plots showing the relationship between bias and subjective Asian population in a state. Each dot represents a state in a certain year. Percent subjectively Asian = $\frac{\# \text{Asian}}{\text{Population}}$ \\
    \emph{Source.} 2004--2021 Current Population Survey.}}
    \end{figure}

### 2025-10-16 submissions/03-jpam-RR/manuscript_tab_fig.tex
finished reviewing intro to data
Save local work before reconnecting

@@

% first
\begin{subfigure}{.9\textwidth}
\caption{Bias Over Time}
\centering
\includegraphics[width=.9\linewidth]{Bias_twostates.png} 
\label{fig:skiniat}
\end{subfigure}
% Second
\begin{subfigure}{.9\textwidth}
\caption{Self-reported Asian Identity Over Time}
\centering
\includegraphics[width=.9\linewidth]{Bias_twostates-asian.png} 
\label{fig:Asian-twostates}
\end{subfigure}
\caption*{\footnotesize{These two panels show the trends in bias (panel a) and self-reported Asian identity among Asian immigrants (panel b) of the least and most biased places in the data. The District of Colombia is the least biased geographical area, and North Dakota is the most biased. The bias units are in standard deviations. Self-reported Asian identity is among first, second, and third-generation Asian immigrants aged 17 and younger still living in intact families.\\
Bias data is from the 2004-2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. Identity data is from the 2004-2021 Current Population Survey (CPS).}}
\end{figure}
\end{center}

@@

\caption*{\footnotesize{This figure shows the state-level bias index in different years in the sample. The bias units are in standard deviations and ranges from low to high bias. Bias index is constructed following \textcite{lubotskyInterpretationRegressionsMultiple2006}. The data is from the 2004-2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. Each panel presents state-level bias during a certain year. The boundaries in black represent the different Census divisions in the United States. Notice how there is a variation across states within a region.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[H]
\caption{Maps of State-level Bias 2004-2021 Measure with Census Division Regional Boundaries}
\includegraphics[width=\textwidth]{Average_Skinmap.png} 
\label{fig:iat-map-all}
\caption*{\footnotesize{This figure shows the state-level bias index in the sample from 2004 to 2021. The bias units are in standard deviations and ranges from low to high bias. Bias index is constructed following \textcite{lubotskyInterpretationRegressionsMultiple2006}. The data is from the 2004-2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. The boundaries in black represent the different Census divisions in the United States. Notice how there is a variation across states within a region.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[H]
\caption{Asian Racial Identity}
\includegraphics[width=\textwidth]{histogram_asian_american_race_aggregated.png} 
\label{fig:histogram-all}
\caption*{\footnotesize{This figure shows the distribution of Asian racial identity among respondents. 
The data is aggregated from the 2004-2021 Current Population Survey (CPS). 
The sample includes first-, second-, and third-generation objectively Asian Americans.
Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, 
I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.
}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[H]
\caption{Asian Racial Identity: First Generation}
\includegraphics[width=\textwidth]{histogram_asian_american_race_firstgen.png} 
\label{fig:histogram-firstgen}
\caption*{\footnotesize{This figure shows the distribution of Asian racial identity among respondents. 
The data is aggregated from the 2004-2021 Current Population Survey (CPS). 
The sample includes first-generation objectively Asian Americans.
Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, 
I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.
A first-generation Asian American is defined as an individual born in an Asian country and is not a US citizen born to US citizen parents abroad.
}}
\end{figure}
\end{center}

@@

\caption*{\footnotesize{This figure shows the distribution of Asian racial identity among respondents. 
The data is aggregated from the 2004-2021 Current Population Survey (CPS). 
The sample includes second-generation objectively Asian Americans.
Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, 
I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.
A second-generation Asian American is defined as a native-born individual with at least one parent born in an Asian country. 
The first panel is for second-generation Asian Americans. The second panel is for second-generation Asian Americans with both parents born in an Asian country. 
The third panel is for second-generation Asian Americans with an Asian father and a White mother. 
The fourth panel is for second-generation Asian Americans with a White father and an Asian mother.
}}
\end{figure}
\end{landscape}

@@

\caption*{\footnotesize{This figure shows the distribution of Asian racial identity among respondents. 
The data is aggregated from the 2004-2021 Current Population Survey (CPS). 
The sample includes second-generation objectively Asian Americans.
Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, 
I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.
A third-generation Asian American is defined as a native-born individual with native-born parents and at least one grandparent born in an Asian country. 
The first panel is for third-generation Asian Americans. The second panel is for third-generation Asian Americans with one grandparent born in an Asian country. 
The third panel is for third-generation Asian Americans with two grandparents born in an Asian country. 
The fourth panel is for third-generation Asian Americans with three grandparents born in an Asian country.
The fifth panel is for third-generation Asian Americans with four grandparents born in an Asian country.
}}
\end{figure}
\end{landscape}

@@

% Marginal Effects: All Generations (after main Multinomial Logit Model plot)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice from Multinomial Logit Model (All Generations)}
\label{fig:marginal-effects-all}
\includegraphics[width=0.9\linewidth]{optimized_marginal_effects_all.png}
\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using a multinomial logit model. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals. The sample includes first-, second-, and third-generation Asian Americans as defined above.}}
\end{figure}
\end{center}

@@

% Marginal Effects: Second Generation by Parental Type (AW and WA)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice by Parental Ancestry (Second-Generation Asian Americans)}
\label{fig:marginal-effects-second-parental}

\begin{subfigure}{.48\textwidth}
\caption{Asian Father-White Mother (AW)}\label{subfig:meaw}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_second_aw.png}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{White Father-Asian Mother (WA)}\label{subfig:mewa}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_second_wa.png}
\end{subfigure}

\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for second-generation Asian Americans by parental ancestry configuration. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent.}}
\end{figure}
\end{center}

@@

% Marginal Effects: Third Generation by Grandparental Type (One, Two, Three Asian Grandparents)
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Marginal Effects of Key Covariates on Racial Identity Choice by Number of Asian Grandparents (Third-Generation Asian Americans)}
\label{fig:marginal-effects-third-grandparental}
\begin{subfigure}{.45\textwidth}
\caption{One Asian Grandparent}\label{subfig:oneasiangrand}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_third_one.png}
\end{subfigure}
\hfill
\begin{subfigure}{.45\textwidth}
\caption{Two Asian Grandparents}\label{subfig:twoasiangrand}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_third_two.png}
\end{subfigure}

\begin{subfigure}{.45\textwidth}
\caption{Three Asian Grandparents}\label{subfig:threeasiangrand}
\centering
\includegraphics[width=1\linewidth]{optimized_marginal_effects_third_three.png}
\end{subfigure}
\caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for third-generation Asian Americans by number of Asian grandparents. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals.}}
\end{figure}
\end{center}

\input{maineffect-proxy}
\pagebreak
\newpage

% \input{tab06-regression_tab_byproxy_skin.tex}
% \pagebreak
% \newpage

\clearpage

>>>>

\input{maineffect-proxy}

@@

% first
\begin{subfigure}{.9\textwidth}
\caption{Bias Over Time}
\centering
\includegraphics[width=.9\linewidth]{Bias_twostates.png} 
\label{fig:skiniat}
\end{subfigure}
% Second
\begin{subfigure}{.9\textwidth}
\caption{Self-reported Asian Identity Over Time}
\centering
\includegraphics[width=.9\linewidth]{Bias_twostates-asian.png} 
\label{fig:Asian-twostates}
\end{subfigure}
\caption*{\footnotesize{These two panels show the trends in bias (panel a) and self-reported Asian identity among Asian immigrants (panel b) of the least and most biased places in the data. The District of Colombia is the least biased geographical area, and North Dakota is the most biased. The bias units are in standard deviations. Self-reported Asian identity is among first, second, and third-generation Asian immigrants aged 17 and younger still living in intact families.\\
Bias data is from the 2004--2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. Identity data is from the 2004--2021 Current Population Survey (CPS).}}
\end{figure}
\end{center}

@@

\caption*{\footnotesize{This figure shows the state-level bias index in different years in the sample. The bias units are in standard deviations and ranges from low to high bias. Bias index is constructed following \textcite{lubotskyInterpretationRegressionsMultiple2006}. The data is from the 2004--2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. Each panel presents state-level bias during a certain year. The boundaries in black represent the different Census divisions in the United States. Notice how there is a variation across states within a region.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[H]
\caption{Maps of State-level Bias 2004--2021 Measure with Census Division Regional Boundaries}
\includegraphics[width=\textwidth]{Average_Skinmap.png} 
\label{fig:iat-map-all}
\caption*{\footnotesize{This figure shows the state-level bias index in the sample from 2004 to 2021. The bias units are in standard deviations and ranges from low to high bias. Bias index is constructed following \textcite{lubotskyInterpretationRegressionsMultiple2006}. The data is from the 2004--2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. The boundaries in black represent the different Census divisions in the United States. Notice how there is a variation across states within a region.}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[H]
\caption{Asian Racial Identity}
\includegraphics[width=\textwidth]{histogram_asian_american_race_aggregated.png} 
\label{fig:histogram-all}
\caption*{\footnotesize{This figure shows the distribution of Asian racial identity among respondents. 
The data is aggregated from the 2004--2021 Current Population Survey (CPS). 
The sample includes first-, second-, and third-generation objectively Asian Americans.
Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, 
I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.
}}
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[H]
\caption{Asian Racial Identity: First Generation}
\includegraphics[width=\textwidth]{histogram_asian_american_race_firstgen.png} 
\label{fig:histogram-firstgen}
\caption*{\footnotesize{This figure shows the distribution of Asian racial identity among respondents. 
The data is aggregated from the 2004--2021 Current Population Survey (CPS). 
The sample includes first-generation objectively Asian Americans.
Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, 
I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.
A first-generation Asian American is defined as an individual born in an Asian country and is not a US citizen born to US citizen parents abroad.
}}
\end{figure}
\end{center}

@@

\caption*{\footnotesize{This figure shows the distribution of Asian racial identity among respondents. 
The data is aggregated from the 2004--2021 Current Population Survey (CPS). 
The sample includes second-generation objectively Asian Americans.
Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, 
I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.
A second-generation Asian American is defined as a native-born individual with at least one parent born in an Asian country. 
The first panel is for second-generation Asian Americans. The second panel is for second-generation Asian Americans with both parents born in an Asian country. 
The third panel is for second-generation Asian Americans with an Asian father and a White mother. 
The fourth panel is for second-generation Asian Americans with a White father and an Asian mother.
}}
\end{figure}
\end{landscape}

@@

\caption*{\footnotesize{This figure shows the distribution of Asian racial identity among respondents. 
The data is aggregated from the 2004--2021 Current Population Survey (CPS). 
The sample includes second-generation objectively Asian Americans.
Following \textcite{antmanEthnicAttritionObserved2016,antmanEthnicAttritionAssimilation2020}, 
I utilize birthplace information for individuals, parents, and grandparents to create objective Asian ancestry indicators.
A third-generation Asian American is defined as a native-born individual with native-born parents and at least one grandparent born in an Asian country. 
The first panel is for third-generation Asian Americans. The second panel is for third-generation Asian Americans with one grandparent born in an Asian country. 
The third panel is for third-generation Asian Americans with two grandparents born in an Asian country. 
The fourth panel is for third-generation Asian Americans with three grandparents born in an Asian country.
The fifth panel is for third-generation Asian Americans with four grandparents born in an Asian country.
}}
\end{figure}
\end{landscape}

@@

% \pagebreak
% \newpage

% % Marginal Effects: All Generations (after main Multinomial Logit Model plot)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice from Multinomial Logit Model (All Generations)}
% \label{fig:marginal-effects-all}
% \includegraphics[width=0.9\linewidth]{optimized_marginal_effects_all.png}
% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using a multinomial logit model. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals. The sample includes first-, second-, and third-generation Asian Americans as defined above.}}
% \end{figure}
% \end{center}

@@

% % Marginal Effects: Second Generation by Parental Type (AW and WA)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice by Parental Ancestry (Second-Generation Asian Americans)}
% \label{fig:marginal-effects-second-parental}

% \begin{subfigure}{.48\textwidth}
% \caption{Asian Father-White Mother (AW)}\label{subfig:meaw}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_second_aw.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.48\textwidth}
% \caption{White Father-Asian Mother (WA)}\label{subfig:mewa}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_second_wa.png}
% \end{subfigure}

% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for second-generation Asian Americans by parental ancestry configuration. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals. Second-generation Asian Americans are native-born individuals with at least one Asian-born parent.}}
% \end{figure}
% \end{center}

% \pagebreak
% \newpage

% =========================
% 41: Multinomial Model - Predicted Probabilities (Adults, AW/WA)
% =========================
\begin{center}
\begin{figure}[!htb]
\centering
\caption{Multinomial Logit Model: Predicted Probabilities of Racial Identity Choice by Key Covariates (Second Generation Adults, AW/WA)}
\label{fig:pp-secondgen-adults-aw-wa}

% Top row: Anti-Asian Bias and Female
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (AW)}
\centering
\includegraphics[width=1\linewidth]{pp_second_aw_value_simple.png}\label{subfig:pp-secgen-aw-bias}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Anti-Asian Bias (WA)}
\centering
\includegraphics[width=1\linewidth]{pp_second_wa_value_simple.png}\label{subfig:pp-secgen-wa-bias}
\end{subfigure}

% Second row: Female
\begin{subfigure}{.48\textwidth}
\caption{Female (AW)}
\centering
\includegraphics[width=1\linewidth]{pp_second_aw_Female_simple.png}\label{subfig:pp-secgen-aw-female}
\end{subfigure}
\hfill
\begin{subfigure}{.48\textwidth}
\caption{Female (WA)}
\centering
\includegraphics[width=1\linewidth]{pp_second_wa_Female_simple.png}\label{subfig:pp-secgen-wa-female}
\end{subfigure}

\caption*{\footnotesize{Predicted probabilities from multinomial logit models for second-generation adults with Asian father/White mother (AW) and White father/Asian mother (WA). Each panel shows the probability of choosing each racial identity as a function of anti-Asian bias or gender, holding other covariates at their means.}}
\end{figure}
\end{center}

@@

% Marginal Effects: Third Generation by Grandparental Type (One, Two, Three Asian Grandparents)
% \begin{center}
% \begin{figure}[!htb]
% \centering
% \caption{Marginal Effects of Key Covariates on Racial Identity Choice by Number of Asian Grandparents (Third-Generation Asian Americans)}
% \label{fig:marginal-effects-third-grandparental}
% \begin{subfigure}{.45\textwidth}
% \caption{One Asian Grandparent}\label{subfig:oneasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_third_one.png}
% \end{subfigure}
% \hfill
% \begin{subfigure}{.45\textwidth}
% \caption{Two Asian Grandparents}\label{subfig:twoasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_third_two.png}
% \end{subfigure}

% \vspace{0.5cm}

% \begin{subfigure}{.45\textwidth}
% \caption{Three Asian Grandparents}\label{subfig:threeasiangrand}
% \centering
% \includegraphics[width=1\linewidth]{optimized_marginal_effects_third_three.png}
% \end{subfigure}
% \caption*{\footnotesize{This figure displays the marginal effects of key covariates on the probability of each racial identification outcome, estimated from equation (\ref{eq:multinomial_logit}) using multinomial logit models for third-generation Asian Americans by number of Asian grandparents. Marginal effects represent the change in predicted probability for a one-unit increase in the covariate (or discrete change from 0 to 1 for binary variables), holding other variables at their sample means. I include region $\times$ year fixed effects with controls for quartic age and local Asian population share. Error bars indicate 95\% confidence intervals.}}
% \end{figure}
% \end{center}

% \pagebreak
% \newpage

### 2025-10-16 submissions/03-jpam-RR/manuscript_title_etc.tex
Save local work before reconnecting

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points across all generations. The effects vary by generation and family type: bias decreases Asian racial identity by 5 percentage points among first-generation immigrants (statistically insignificant), 8 percentage points among second-generation, and 8 percentage points among third-generation Asian Americans. Mixed-race families show the strongest responses, with bias decreasing Asian racial identity by 15 percentage points among children of Asian fathers and White mothers, and 10 percentage points among children of White fathers and Asian mothers. Using multinomial logit regression, I find that high bias environments drive substantial shifts from ``Asian only'' to ``White only'' racial identity, with probabilities changing by up to 50 percentage points. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and the correct counting of the population.
\PAPERJEL}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. Using a multiple proxy regression approach, I construct a bias measure based on the Implicit Association Test (IAT), the American National Election Studies (ANES), and hate crimes against Asians. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points across all generations. The effects vary by generation and family type: bias decreases Asian racial identity by 5 percentage points among first-generation immigrants (statistically insignificant), 8 percentage points among second-generation, and 8 percentage points among third-generation Asian Americans. Mixed-race families show the strongest responses, with bias decreasing Asian racial identity by 15 percentage points among children of Asian fathers and White mothers, and 10 percentage points among children of White fathers and Asian mothers. Using multinomial logit regression, I find that high bias environments drive substantial shifts from ``Asian only'' to ``White only'' racial identity, with probabilities changing by up to 50 percentage points. Higher parental education and income generally increase the probability of reporting Asian identity, with particularly strong effects among mixed-race children. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and accurate population measurement. \PAPERJEL}
